\documentclass{beamer}
\usetheme{Goettingen}
\usecolortheme{sidebartab}
\usepackage{hyperref}


\makeatletter
\makeatother
\title{Experience in MCM2022}
\author{Zhirong Chen, Ziyuan Chen}
\institute{ZJUI Institute}
\date{2023/2/10}


\AtBeginSection[] {
    \begin{frame}
        \frametitle{Table of Contents}
        \tableofcontents[currentsection]
    \end{frame}
}


\begin{document}


\frame{\titlepage}
\begin{frame}
    \frametitle{Contents}
    \begin{itemize}
        \setlength{\itemsep}{20pt}
        \setlength{\parsep}{6pt}
        \setlength{\parskip}{3pt}
        \item Preparation
        \item During the Contest
        \item Paper Writing
    \end{itemize}
\end{frame}


\begin{frame}
    \frametitle{Introduction}
    \framesubtitle{Capacity}
    \begin{itemize}
        \setlength{\itemsep}{7pt}
        \item Team Working
        \begin{itemize}
            \item Tip: 80\% + 20\%
        \end{itemize}
        \item Mathematical Thinking
        \item Paper Writing
    \end{itemize}
\end{frame}


\begin{frame}
    \frametitle{Preparation}
    \framesubtitle{What should you do?}
    \begin{enumerate}
        \item Read through any mathematical modeling book
        \begin{itemize}
            \item \textit{Python Mathematical Experiment and Modeling}
            \item "Writing the MCM paper correctly"
            \item ...
        \end{itemize}
        \item Useful python libraries
        \begin{itemize}
            \item \textbf{Data Processing:} pandas, statsmodels
            \item \textbf{Modelling:} scipy, sympy
            \item \textbf{Machine Learning:} sklearn, pytorch
            \item \textbf{Data Visualization:} matplotlib, seaborn
        \end{itemize}
        \item Try to learn \LaTeX
    \end{enumerate}
\end{frame}


\begin{frame}
    \frametitle{Preparation}
    \framesubtitle{What's next?}
    \begin{enumerate}
        \setlength{\itemsep}{5pt}
        \item Traditional Modelling Algorithms
        \begin{itemize}
            \setlength{\itemsep}{5pt}
            \item analytic hierarchy process
            \item PCA (principal component analysis)
        \end{itemize}
        \item{Advanced Modelling Algorithms}
        \begin{itemize}
            \setlength{\itemsep}{5pt}
            \item ant colony algorithm
            \item genetic algorithm
        \end{itemize}
        \item Paper Writing Skill
    \end{enumerate}
    \alert{Attention: Don't use too many neural networks in your model}, because
    \begin{enumerate}
        \item they usually don't have good interpretability
        \item sometimes they are not suitable for the data
    \end{enumerate}
\end{frame}


\begin{frame}
    \frametitle{During the Contest}
    \framesubtitle{\textit{The} Three Pillars}
    \begin{itemize}
        \setlength{\itemsep}{5pt}
        \item Modeling
        \item Coding
        \item Writing
    \end{itemize}
    \vspace{20pt}
    \begin{itemize}
        \setlength{\itemsep}{5pt}
        \item Be sure to help each other out
        \item ...
    \end{itemize}
\end{frame}


\begin{frame}
    \frametitle{During the Contest}
    \framesubtitle{Our solution}
    \begin{itemize}
        \setlength{\itemsep}{5pt}
        \item \textbf{Ziyuan Chen:} Prediction, \textit{Visualization}, Paper Writing
        \item \textbf{Zhirong Chen:} Decision I (CAPM), \textit{Parameter Tuning}
        \item \textbf{Zicheng Ma:} Decision II (LinProg), \textit{Sensitivity Analysis}
    \end{itemize}
    \vspace{20pt}
    \begin{itemize}
        \setlength{\itemsep}{5pt}
        \item Be sure to help each other out
        \item and be \textbf{prepared} to help each other out
    \end{itemize}
\end{frame}


\begin{frame}
    \frametitle{During the Contest}
    \framesubtitle{Prepare for the unexpected}
    \begin{itemize}
        \setlength{\itemsep}{10pt}
        \item We don't know much about \textit{finance}
        \begin{itemize}
            \item or technically every possible topic
        \end{itemize}
        \item When \href{https://www.mathmodels.org/Problems/2022/MCM-C/2022_Problem_C_DATA.zip}{data} runs out (yeah, it happens)
        \begin{itemize}
            \item and \textbf{37\%} of all teams choose the same problem......
        \end{itemize}
    \end{itemize}
\end{frame}


\begin{frame}
    \frametitle{Paper Writing}
    \begin{itemize}
        \setlength{\itemsep}{10pt}
        \item \LaTeX $\textrm{ }$ is \textbf{good}.
        \begin{itemize}
            \item It helps to have an expert.
        \end{itemize}
        \item Beautiful formatting is \textbf{good}.
        \begin{itemize}
            \item Make use of templates and packages.
            \item It's not AAAI or IEEE, but there's a \href{https://www.ctan.org/pkg/mcmthesis}{\verb|mcmthesis}
        \end{itemize}
        \item Graphs are \textbf{good}.
        \begin{itemize}
            \item Think twice, though.
        \end{itemize}
        \item Teamwork is the \textbf{best}.
        \begin{itemize}
            \item Everyone should contribute. Everyone.
        \end{itemize}
    \end{itemize}
\end{frame}


\begin{frame}
    \frametitle{Takeaway Points}
    \begin{itemize}
        \item \textbf{Be diverse.} Why not try it out?
        \begin{itemize}
            \item ARIMA, GM, MLP, CAPM, LinProg, AHP......
        \end{itemize}
        \item \textbf{Be structured.} Feel good about your product.
        \begin{itemize}
            \item Prediction + Decision
        \end{itemize}
        \item \textbf{Be specific.} Your model doesn't work for all.
        \begin{itemize}
            \item Long/short term, \#sample, etc.
        \end{itemize}
        \item \textbf{Be considerate.} Mind the details.
        \begin{itemize}
            \item e.g. What data will we have \textit{in the future}?
        \end{itemize}
        \item \textbf{Be creative.} Think more and stand out.
        \begin{itemize}
            \item ``Eyesight'' and ``risk tolerance'' in our case
        \end{itemize}
    \end{itemize}
\end{frame}


\begin{frame}
    \frametitle{Additional Resources}
    \href{https://github.com/AllenHeartcore/MCM2022_2214713}{\verb|https://github.com/AllenHeartcore/MCM2022\_2214713}
\end{frame}


\end{document}
